---
title: "Board Game Statistics"
author: "Kenneth Lee Osborne III"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bgStats)
```

# Introduction

The purpose of this package is to be able to download and inspect the details of board game playing patterns. The idea came from looking at the paltry statistics generated by the beautiful app BG Stats, an app that I use for logging the board games that I'm playing throughout 2020. (Note that plays can be logged with other apps, or on the Board Game Geek website directly also.)

As an overview, the first thing that I do is pull BGG user data from their wonderful xml api. I load that data into an R data frame and then proceed to calculate all sorts of entirely random statistics. 

At the end of the day I make pretty tables and figures that all automatically populate into a shiny app.
